The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-26 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{deluxetable}{lll}
    \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
    \tablehead{
        \colhead{Source} & \colhead{Element} & \colhead{Yield}
    }
    \startdata
    CCSN    & O     & 0.015     \\
    CCSN    & Fe    & 0.0012    \\
    \hline
    SN Ia   & O     & 0         \\
    SN Ia   & Fe    & 0.00214   \\
    \enddata
\end{deluxetable}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
    \\
    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
    \caption{}
    \label{fig:onezone-multipanel}
    \script{onezone_multipanel.py}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_powerlaw_slope.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. The open symbols located along each curve mark logarithmic steps in simulation time. In all cases a minimum SN Ia delay time of 40 Myr is assumed. \textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models. \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-powerlaw-slope}
    \script{onezone_powerlaw_slope.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_exponential_timescale.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD. The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
    \label{fig:onezone-exponential-timescale}
    \script{onezone_exponential_timescale.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/onezone_plateau_width.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD. The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively. All plateau DTDs assume a power-law slope of $\alpha=-1.1$. For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
    \label{fig:onezone-plateau-width}
    \script{onezone_plateau_width.py}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/onezone_twopopulation.pdf}
    \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
    \label{fig:onezone-prompt}
    \script{onezone_twopopulation.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_dtd.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
    \label{fig:onezone-dtd}
    \script{onezone_dtd.py}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_minimum_delay.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$). Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr. The red curves represent a power-law DTD with slope $\alpha=-1.1$; blue curves represent an plateau DTD with width $W=0.3$ Gyr and slope $\alpha=-1.1$; and orange curves represent an exponential DTD with timescale $\tau=3$ Gyr. In all cases an exponential rise-fall SFR is assumed.}
    \label{fig:onezone-minimum-delay}
    \script{onezone_minimum_delay.py}
\end{figure}

@@

\subsection{Analytical Formulations}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row. All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

@@

\subsection{The distribution of [O/Fe]}

>>>>

\begin{deluxetable}{lll}
    \tablecaption{Nucleosynthetic yields assumed in our simulations.\label{tab:yields}}
    \tablehead{
        \colhead{Source} & \colhead{Element} & \colhead{Yield}
    }
    \startdata
    CCSN    & O     & 0.015     \\
    CCSN    & Fe    & 0.0012    \\
    \hline
    SN Ia   & O     & 0         \\
    SN Ia   & Fe    & 0.00214
    \enddata
\end{deluxetable}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.32\linewidth]{figures/onezone_powerlaw_slope.pdf}
    \includegraphics[width=0.32\linewidth]{figures/onezone_exponential_timescale.pdf}
    \includegraphics[width=0.32\linewidth]{figures/onezone_plateau_width.pdf}
    \includegraphics[width=0.49\linewidth]{figures/onezone_minimum_delay.pdf}
    \includegraphics[width=0.49\linewidth]{figures/onezone_dtd.pdf}
    \caption{\textit{Top left:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. The open symbols located along each curve mark logarithmic steps in simulation time. In all cases a minimum SN Ia delay time of 40 Myr is assumed. The marginal panels above and to the right present the distributions of [Fe/H] and [O/Fe], respectively, convolved with a Gaussian with a standard deviation of 0.02 dex for display purposes.
    \textit{Top middle:} A similar plot comparing exponential DTDs with varying timescales. The solid, dashed, and dotted curves represent timescales $\tau=6$, 3, and 1.5 Gyr, respectively.
    \textit{Top right:} Similar, comparing plateau DTDs with varying plateau widths. The solid, dashed, and dotted curves represent widths $W=1$, 0.3, and 0.1 Gyr, respectively. All plateau DTD models assume a post-plateau power-law slope of $\alpha=-1.1$. For reference, the dotted purple curve represents an exponential DTD with $\tau=3$ Gyr, and the dotted blue curve represents a power-law DTD $\alpha=-1.1$ and no plateau.
    \textit{Bottom left:} A similar plot comparing minimum SN Ia delay times of 40 Myr (solid) and 150 Myr (dashed) for two DTDs: a power-law with $\alpha=-1.1$ (blue), and an exponential with $\tau=1.5$ Gyr (purple).
    \textit{Bottom right:} A similar plot comparing all five functional forms for the DTD in this paper: triple-system (green), plateau with $W=1$ Gyr (cyan), exponential with $\tau=1.5$ Gyr (purple), power-law with $\alpha=-1.1$ (blue), and two-population (pink). In all cases a minimum SN Ia delay time of 40 Myr is assumed.}
    \label{fig:onezone-multipanel}
    \script{onezone_multipanel.py}
\end{figure*}

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_powerlaw_slope.pdf}
%     \caption{\textit{Center:} Abundance tracks in the [Fe/H]--[O/Fe] plane for one-zone models with a power-law DTD. The dotted, dashed, and solid curves represent models with power-law slopes $\alpha=-0.8$, $-1.1$, and $-1.4$, respectively. The open symbols located along each curve mark logarithmic steps in simulation time. In all cases a minimum SN Ia delay time of 40 Myr is assumed. \textit{Top:} Metalliticy distribution functions (MDFs) generated by the one-zone models. \textit{Right:} Distributions of [O/Fe] generated by the one-zone models.}
%     \label{fig:onezone-powerlaw-slope}
%     \script{onezone_powerlaw_slope.py}
% \end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_exponential_timescale.pdf}
%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with an exponential DTD. The dotted, dashed, and solid curves represent exponential decay timescales $\tau=1.5$ Gyr, 3 Gyr, and 6 Gyr, respectively.}
%     \label{fig:onezone-exponential-timescale}
%     \script{onezone_exponential_timescale.py}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_plateau_width.pdf}
%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but for one-zone models with a plateau DTD. The solid, dashed, and dot-dashed pink curves represent plateau widths $W=1.0$, 0.3, and 0.1 Gyr, respectively. All plateau DTDs assume a power-law slope of $\alpha=-1.1$. For comparison, the blue dotted curve represents an exponential DTD with a timescale $\tau=3$ Gyr, and the black dotted curve represents a power-law DTD with the same slope but no plateau.}
%     \label{fig:onezone-plateau-width}
%     \script{onezone_plateau_width.py}
% \end{figure}

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_twopopulation.pdf}
%     \caption{One-zone model abundance tracks and distributions for variants of the two-population DTD.}
%     \label{fig:onezone-prompt}
%     \script{onezone_twopopulation.py}
% \end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_dtd.pdf}
%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with a different selection of DTDs. In all cases a minimum delay time of 40 Myr is assumed.}
%     \label{fig:onezone-dtd}
%     \script{onezone_dtd.py}
% \end{figure}

@@

% \begin{figure}
%     \centering
%     \includegraphics{figures/onezone_minimum_delay.pdf}
%     \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$). Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr. The red curves represent a power-law DTD with slope $\alpha=-1.1$; blue curves represent an plateau DTD with width $W=0.3$ Gyr and slope $\alpha=-1.1$; and orange curves represent an exponential DTD with timescale $\tau=3$ Gyr. In all cases an exponential rise-fall SFR is assumed.}
%     \label{fig:onezone-minimum-delay}
%     \script{onezone_minimum_delay.py}
% \end{figure}

@@

@@

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row. All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}
\subsection{The distribution of [O/Fe]}
